Some examples in extended logic counting classes

### 2016-04-20 tex/below.tex
20 abr

	\begin{algorithm}

	\begin{algorithmic}[]
		\Begin
		\If{$f(x) = 0$} stop
		\Else \text{ choose from}
		\State stop
		\State call $\textsc{GenTree}_{f}(x,\{s_0\},\epsilon)$
		\EndIf
		\EndBegin
		\Procedure{$\textsc{GenTree}_{f}(x,S,y)$}{}
		\State $S_0 = \emptyset$, $S_1 = \emptyset$
		\For{$s\in S$}
		\State do a search in the configuration graph of $M$ with input $x$ from $s$:
		\If{$s'$ is reached after writing 0 in the output tape} $S_0 \gets s'$
		\EndIf
		\If{$s'$ is reached after writing 1 in the output tape} $S_1 \gets s'$
		\EndIf
		\EndFor
		\If{a final state from $M$ is reachable from some $s\in S_0$ and some $s'\in S_1$} choose between:
		\State call $\textsc{GenTree}_{f}(x,S_0,y0)$
		\State call $\textsc{GenTree}_{f}(x,S_1,y1)$
		\ElsIf{a final state from $M$ is reachable from some $s\in S_i$ but not from any $s'\in S_{1-i}$}
		\State call $\textsc{GenTree}_{f}(x,S_i,yi)$
		\ElsIf{no final state from $M$ is reachable from any $s\in S_0 \cup S_1$}
		\Return $y$
		\EndIf
		\EndProcedure
	\end{algorithmic}

	\end{algorithm}

	We use $s_0$ for the initial state of $M$ with input $x$. The algorithm can be executed in a nondeterministic polynomial-time machine, so we only need to show that the number of computation paths is equal to $\sp_M(x)+1$.

>>>>

	\begin{algorithm}	
	\caption{Compute $f(x)+1$ paths}
	\begin{algorithmic}[]
		\Begin
		\If{$f(x) = 0$} stop
		\Else \text{ choose from}
		\State stop
		\State call $\textsc{GenTree}_{f}(x,\{s_0\},\epsilon)$
		\EndIf
		\EndBegin
		\Procedure{$\textsc{GenTree}_{f}(x,S,y)$}{}
		\State $S_0 = \emptyset$, $S_1 = \emptyset$
		\For{$s\in S$}
		\State do a search in the configuration graph of $M$ with input $x$ from $s$:
		\If{$s'$ is reached after writing 0 in the output tape} $S_0 \gets s'$
		\EndIf
		\If{$s'$ is reached after writing 1 in the output tape} $S_1 \gets s'$
		\EndIf
		\EndFor
		\If{a final state from $M$ is reachable from some $s\in S_0$ and some $s'\in S_1$} choose between:
		\State call $\textsc{GenTree}_{f}(x,S_0,y0)$
		\State call $\textsc{GenTree}_{f}(x,S_1,y1)$
		\ElsIf{a final state from $M$ is reachable from some $s\in S_i$ but not from any $s'\in S_{1-i}$}
		\State call $\textsc{GenTree}_{f}(x,S_i,yi)$
		\ElsIf{no final state from $M$ is reachable from any $s\in S_0 \cup S_1$}
		\Return $y$
		\EndIf
		\EndProcedure
	\end{algorithmic}
	\end{algorithm}

	We use $s_0$ for the initial state of $M$ with input $x$. The algorithm can be executed in a nondeterministic polynomial-time machine, so we only need to show that the number of computation paths is equal to $\sp_M(x)-1$.

### 2016-04-20 tex/pe.tex
20 abr

@@

Let $M$ be a unary second-order variable, and
\begin{align*}
\varphi(M) &= \forall x \forall y (M(x,y)\to E(x,y))\,\wedge \\
& \forall x \forall y (M(x,y)\to x < y)\,\wedge \\
& \forall x \forall y \forall z(M(x,y)\wedge M(z,y) \to x = z)\,\wedge \\
& \forall x \forall y \forall z(M(x,y)\wedge M(x,z) \to y = z)\,\wedge \\
& \forall x \forall y \forall z(\neg M(x,y)\vee \neg M(y,z)).
\end{align*}
Therefore, $f_{\varphi(M)}(\A)$ counts the number of matchings in $G$.
\subsection{\#2SAT}

>>>>

We now show that \#Clique belongs to {\totp } with a non-deterministic machine $M$ which we present as a non-deterministic algorithm that takes $G = (V,E)$ as input. We further suppose that $V = \{1,...,n\}$.

	\begin{algorithm}	
		\caption{Compute $\text{\#Clique}(G)+1$ paths}
		\begin{algorithmic}[]
			\Begin
			\If{$G = \emptyset$} stop
			\Else \text{ choose} $v\in V\cup\{\perp\}$ 
			\If{$v = \perp$} stop
			\Else \text{ call} $\textsc{GenTree}(G,\emptyset)$
			\EndIf
			\EndIf
			\EndBegin
			\Procedure{$\textsc{GenTree}(G,S)$}{}
			\State $u \gets$ the last vertex in $S$
			\State $T = \emptyset$
			\For{$v \in \{u+1,\dots,n\}$}
			\If{$v$ is connected to each $u'\in S$}
			\State $T \gets v$
			\EndIf
			\EndFor
			\If{$T \neq \emptyset$} choose $v'\in T\cup\{\perp\}$
			\If{$v' = \perp$} stop
			\Else \text{ call} $\textsc{GenTree}(G,S\cup\{v'\})$
			\EndIf
			\Else \text{ stop}
			\EndIf
			\EndProcedure
		\end{algorithmic}
	\end{algorithm}

At each point in the computation $S$ contains the vertices of a clique in $G$, and since the computation follows the order of the vertices in $G$, every clique is counted exactly once.

@@

Let $M$ be a unary second-order variable, and
\begin{align*}
\varphi(M) &= \forall x \forall y (M(x,y)\to E(x,y))\,\wedge \\
& \forall x \forall y (M(x,y)\to x < y)\,\wedge \\
& \forall x \forall y \forall z(M(x,y)\wedge M(z,y) \to x = z)\,\wedge \\
& \forall x \forall y \forall z(M(x,y)\wedge M(x,z) \to y = z)\,\wedge \\
& \forall x \forall y \forall z(\neg M(x,y)\vee \neg M(y,z)).
\end{align*}
Therefore, $f_{\varphi(M)}(\A)$ counts the number of matchings in $G$.

\subsection{\#2SAT}
